Bandit Multiclass Classification

### 2018-07-18 main.tex
Add Sec 1-3

It turns out this specific 1-dimensional problem is equivalent to check whether there is a \textbf{missing permutation} of $[K]$ / find a missing permutation in the given subsequence. In example 1, the existed permutations are $(1,2,3), (1,3,2), (2,3,1), (3,1,2)$, the missing ones are $(2,1,3)$ and $(3,2,1)$.  So the solutions can be $(2,1,3)$ or $(3,2,1)$ (with some repetition). In Example 2, all permutations are as subsequences, so there is no solution.

>>>>

It turns out this specific 1-dimensional problem is equivalent to identify a \textbf{missing permutation} of $[K]$ as a subsequence in the given sequence. In Example 1, the existing permutations are $(1,2,3), (1,3,2), (2,3,1), (3,1,2)$, the missing ones are $(2,1,3)$ and $(3,2,1)$.  So the solutions can be $(2,1,3)$ or $(3,2,1)$ (with some repetition). In Example 2, all permutations are as subsequences, so there is no solution.
